---
title: "YESWANTH SIRIPURAPU R Notebook"
output:
  pdf_document: default
  html_notebook: default
  word_document: default
---

#Install the ISLR PACKAGE
```{r}
library("ISLR")
```


# With this line of code, a summary of the "Carseats" dataset is produced. 
#The summary() method offers a number of statistics and details about the 
#variables in the dataset. For numerical variables, it will show measurements
#like mean, median, minimum, maximum, and quartiles; for categorical variables,
#it will show counts. Understanding the properties of the dataset in general 
#is made easier by reading this summary.The number of rows in the "Carseats" 
#dataset are determined by the statement nrow(Carseats). The entire number of 
#observations or data points in the dataset is returned, in other words.

```{r}

summary(Carseats)
nrow(Carseats)
```
# The greatest value in the "Advertising" column of the "Carseats" dataset will
#be returned by this line. It will specifically provide you the observation in 
#the dataset with the highest average advertising expenditure.

```{r}
max(Carseats $ Advertising)

```
```{r}
IQR(Carseats $ Price)
```
 

#The code plots the sales of carseats over time, and the price.
#The main is "sales v/s Price".
#The x-axis shows the number of cars seats sold in a given year.
#The y-axis shows how much each car seat cost at that time.
#The code creates a scatter plot of the data from Carseats.
#The code also includes a title, main, and x-axis label.


```{r}
plot(Carseats$`Sales`,Carseats$`Price`,
     main = "sales v/s Price",
     xlab = "sales",
     ylab = "Price",
     col= "red")


```
#The code starts by creating a list of cars that are available for sale.
#The code then creates a new variable called "Carseats" which is the name of the
#data set and contains all the information about each car.
#Next, it creates another new variable called "Sales" which is an array
#containing all the sales prices for each car.
# Finally, it calculates the correlation between Sales and Price using cor()
#function in R programming language.
# The first if statement checks to see if there is a positive correlation between
#Sales and Price (correlation > 0).
# If there was no correlation greater than zero, then this would mean that there
#No linear relationship between these two variables (no linear relationship)
#The code will print "The correlation is close to zero (no linear relationship).
#If the correlation between Carseats$Sales and Carseats$Price is less than 0.5.


```{r}
correlation <- cor(Carseats$Sales, Carseats$Price)
correlation
if (correlation > 0) {
  cat("The correlation is positive.\n")
} else if (correlation < 0) {
  cat("The correlation is negative.\n")
} else {
  cat("The correlation is close to zero (no linear relationship).\n")
}
  
```